A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-28 paper.tex
Added benchmark plots for us and demiurge

@@

INSERT GRAPHS

>>>>

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[y=0.04cm, x=0.15cm]
        %axis
        \draw (0,0) -- coordinate (x axis mid) (60,0);
            \draw (0,0) -- coordinate (y axis mid) (0,150);
            %ticks
            \foreach \x in {0,10,...,60}
                \draw (\x,1pt) -- (\x,-3pt)
                node[anchor=north] {\x};
            \foreach \y in {0,25,...,150}
                \draw (1pt,\y) -- (-3pt,\y) 
                    node[anchor=east] {\y}; 
        %labels      
        \node[below=0.8cm] at (x axis mid) {Time (min)};
        \node[rotate=90, above left=1cm and 0.7cm] at (y axis mid) {Instances solved};

        %Plots
        \draw plot[mark=x, mark options={fill=white}] file {bench_termite.dat};
        \draw plot[mark=+, mark options={fill=white}] file {bench_demiurge.dat};

        \begin{scope}[shift={(30,20)}] 
            \draw (0,0) -- 
                plot[mark=x, mark options={fill=white}] (0.25,0) -- (0.5,0) 
                node[right]{Unbounded synthesis};
            \draw[yshift=\baselineskip] (0,0) -- 
                plot[mark=+, mark options={fill=white}] (0.25,0) -- (0.5,0)
                node[right]{Demiurge};
        \end{scope}

    \end{tikzpicture}
\end{figure}

@@
